### 2016-06-27 lineups.Rnw
couple of questions

@@

After the lineups were created, we also re-fit each of our three models to each graph in each lineup.

>>>>

\hh{Needs more specifics: how many lineups were created for each model?}

\hh{At the moment we are just considering models M2 and M3 for an inclusion in the lineup study. We are trying to nail down what to include and what not to include in the experiment.  }

@@

After the lineups were created, we re-fit each of our three models to each graph in each lineup.

\hh{Questions that should be answered in this section:

1. Why do we want to get the parameters for each model?

2. How is the fitting done, exactly?

4. What parameters are in the output?

5. What are the results?

6. How do the results influence our decision for the lineups?

}
